Fossil-calibrated phylogeny of Onagraceae: patterns of floral and chromosome evolution

### 2014-05-02 manuscript.tex
set up make rtf for word docs
added correlation results

\usepackage{lineno}
\usepackage[hidelinks]{hyperref}
\usepackage{mathtools}
\usepackage{adjustbox}

\modulolinenumbers[5]

@@

\begin{table*}
   \begin{adjustbox}{max width=\textwidth}
      \begin{tabular}{lllllll}
         \hline
         Group & Age (Mya) & Prior Distribution & Mean & SD & Offset & Reference \\ 
	 \hline
         \textit{Circaea} (Onagraceae) & 12 & lognormal & 0.0 & 2.0 & 12 & \citep{grimsson} \\
         \textit{Epilobium} (Onagraceae) & 12 & lognormal & 0.0 & 2.0 & 12 & \citep{grimsson} \\
         S. Pacific \textit{Fuschia} (Onagraceae) & 23 & lognormal & 0.0 & 1.0 & 23 & \citep{lee2013fossil} \\
         \textit{Ludwigia} (Onagraceae) & Paleocene & normal & 60.0 & 3.0 & - & \citep{zhi} \\
         Lythraceae & 82 & lognormal & 0.0 & 2.0 & 82 & \citep{graham} \\
         \hline
      \end{tabular}
   \end{adjustbox}
   \caption{Fossils used as priors in the Bayesian divergence time analysis.}
   \label{fossils}
\end{table*}

@@

\begin{table*}
   \begin{adjustbox}{max width=\textwidth}
      \begin{tabular}{lllllll}
         \hline
         DNA Region & \# of Taxa & Aligned Length & Missing data (\%) & Taxon Coverage Density \\ 
	 \hline
         ITS & 453 & 1746 & 13.2 & 0.87 \\
         trnL & 234 & 1429 & 55.2 & 0.45 \\
         rpl16 & 91 & 1414 & 82.6 & 0.17 \\
         rbcL & 77 & 1474 & 85.2 & 0.15 \\
         rps16 & 74 & 1016 & 85.8 & 0.14 \\
         rbcL & 64 & 1310 & 87.7 & 0.12 \\
         PgiC2 & 47 & 4028 & 91.0 & 0.09 \\
         matK & 37 & 921 & 92.9 & 0.07 \\
         ndhF & 37 & 2063 & 92.9 & 0.07 \\
         pgiC & 26 & 14709 & 95.0 & 0.05 \\
         R5 & 18 & 3129 & 96.6 & 0.03 \\
         \hline
      \end{tabular}
   \end{adjustbox}
   \caption{Clusters of homologous sequences used to assemble the supermatrix.}
   \label{clusters}
\end{table*}

@@

\begin{table*}
   \begin{adjustbox}{max width=\textwidth}
      \begin{tabular}{lllllll}
         \hline
         Clade & Mean Age (Mya) & 95\% HPD Min & 95\% HPD Max \\ 
	 \hline
         Onagraceae / Lythraceae & 109 & 88 & 131 \\
         \textit{Ludwigia} & 97 & 76 & 118 \\
	 \textit{Hauya} & 49 & 35 & 64 \\
	 \textit{Circaea} / \textit{Fuchshia} & 37 & 28 & 47 \\
	 \textit{Lopezia} & 71 & 55 & 68 \\
	 \textit{Gongylocarpus} & 60 & 45 & 77 \\
	 \textit{Epilobium} & 49 & 38 & 60 \\
	 \textit{Chamerion} & 47 & 36 & 57 \\
	 \textit{Xylonagra} & 43 & 33 & 52 \\
	 \textit{Clarkia} & 40 & 32 & 48 \\
         \textit{Terapteron} & 19 & 10 & 29 \\
	 \textit{Camissoniopsis} / \textit{Neoholmgrenia} & 14 & 5 & 23 \\
	 \textit{Eremothera} / \textit{Camissonia} & 24 & 16 & 33 \\
	 \textit{Taraxia} & 30 & 22 & 38 \\
	 \textit{Chylismiella} / \textit{Gayophytum} & 20 & 10 & 30 \\
	 \textit{Eulobus} & 26 & 19 & 34 \\
	 \textit{Chylismia} / \textit{Oenothera} & 25 & 18 & 31 \\
         \hline
      \end{tabular}
   \end{adjustbox}
   \caption{Bayesian divergence time estimates of major clades.}
   \label{times}
\end{table*}

@@

>>>>

\usepackage{lineno}
\usepackage[hidelinks]{hyperref}
\usepackage{mathtools}
\usepackage{adjustbox}
\usepackage{natbib}
\modulolinenumbers[5]

@@

\begin{table*}
   \center
   \begin{adjustbox}{max width=\textwidth}
      \begin{tabular}{lllllll}
         \hline
         Group & Age (Mya) & Prior Distribution & Mean & SD & Offset & Reference \\ 
	 \hline
         \textit{Circaea} (Onagraceae) & 12 & lognormal & 0.0 & 2.0 & 12 & \citep{grimsson} \\
         \textit{Epilobium} (Onagraceae) & 12 & lognormal & 0.0 & 2.0 & 12 & \citep{grimsson} \\
         S. Pacific \textit{Fuschia} (Onagraceae) & 23 & lognormal & 0.0 & 1.0 & 23 & \citep{lee2013fossil} \\
         \textit{Ludwigia} (Onagraceae) & Paleocene & normal & 60.0 & 3.0 & - & \citep{zhi} \\
         Lythraceae & 82 & lognormal & 0.0 & 2.0 & 82 & \citep{graham} \\
         \hline
      \end{tabular}
   \end{adjustbox}
   \caption{Fossils used as priors in the Bayesian divergence time analysis.}
   \label{fossils}
\end{table*}

@@

\begin{table*}
   \center
   \begin{adjustbox}{max width=\textwidth}
      \begin{tabular}{lllllll}
         \hline
         DNA Region & \# of Taxa & Aligned Length & Missing data (\%) & Taxon Coverage Density \\ 
	 \hline
         ITS & 453 & 1746 & 13.2 & 0.87 \\
         trnL & 234 & 1429 & 55.2 & 0.45 \\
         rpl16 & 91 & 1414 & 82.6 & 0.17 \\
         rbcL & 77 & 1474 & 85.2 & 0.15 \\
         rps16 & 74 & 1016 & 85.8 & 0.14 \\
         rbcL & 64 & 1310 & 87.7 & 0.12 \\
         PgiC2 & 47 & 4028 & 91.0 & 0.09 \\
         matK & 37 & 921 & 92.9 & 0.07 \\
         ndhF & 37 & 2063 & 92.9 & 0.07 \\
         pgiC & 26 & 14709 & 95.0 & 0.05 \\
         R5 & 18 & 3129 & 96.6 & 0.03 \\
         \hline
      \end{tabular}
   \end{adjustbox}
   \caption{Clusters of homologous sequences used to assemble the supermatrix.}
   \label{clusters}
\end{table*}

@@

\begin{table*}
   \center
   \begin{adjustbox}{max width=\textwidth}
      \begin{tabular}{lllllll}
         \hline
         Clade & Mean Age (Mya) & 95\% HPD Min & 95\% HPD Max \\ 
	 \hline
         Onagraceae / Lythraceae & 109 & 88 & 131 \\
         \textit{Ludwigia} & 97 & 76 & 118 \\
	 \textit{Hauya} & 49 & 35 & 64 \\
	 \textit{Circaea} / \textit{Fuchshia} & 37 & 28 & 47 \\
	 \textit{Lopezia} & 71 & 55 & 68 \\
	 \textit{Gongylocarpus} & 60 & 45 & 77 \\
	 \textit{Epilobium} & 49 & 38 & 60 \\
	 \textit{Chamerion} & 47 & 36 & 57 \\
	 \textit{Xylonagra} & 43 & 33 & 52 \\
	 \textit{Clarkia} & 40 & 32 & 48 \\
         \textit{Terapteron} & 19 & 10 & 29 \\
	 \textit{Camissoniopsis} / \textit{Neoholmgrenia} & 14 & 5 & 23 \\
	 \textit{Eremothera} / \textit{Camissonia} & 24 & 16 & 33 \\
	 \textit{Taraxia} & 30 & 22 & 38 \\
	 \textit{Chylismiella} / \textit{Gayophytum} & 20 & 10 & 30 \\
	 \textit{Eulobus} & 26 & 19 & 34 \\
	 \textit{Chylismia} / \textit{Oenothera} & 25 & 18 & 31 \\
         \hline
      \end{tabular}
   \end{adjustbox}
   \caption{Bayesian divergence time estimates of major clades.}
   \label{times}
\end{table*}

@@

\begin{table*}
   \center
   \begin{adjustbox}{max width=\textwidth}
      \begin{tabular}{l|llllll}
         \hline
	 & \multicolumn{4}{c}{Number of Petals} \\
         Color & 2 & 4 & 5 & 6 \\ 
	 \hline
         pink & -0.005 & .011 & ns & ns \\
	 yellow & -0.008 & .021 & ns & ns \\
	 white & 0.008 & 0.013 & -0.006 & -0.006 \\
	 green & ns & -0.011 & ns & ns \\
	 red & ns & ns & ns & ns \\
         \hline
      \end{tabular}
   \end{adjustbox}
   \caption{Test statistics for the correlation between flower color and number of petals. 
	    $d$ values are shown
            for the pairwise comparison of states with $p< 0.05$. ns indicates no significant
	    association. The overall $D$ value was 0.263 ($p=0.00$).
	    }
   \label{correlations}
\end{table*}
